Figure 2 and figure 2 supplementary material

### 2022-03-10 Figures/Figure2.Rmd
order Figure2 corrplot by mean

    # Plot
    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|"))) %>% 
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}

>>>>

    # Plot
    store_corrs <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|")))

    order <- store_corrs %>% group_by(measure2) %>% dplyr::summarize(meanr = mean(r)) %>% arrange(desc(meanr))
    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange( factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}
